---
title: "Calculation of DIstance"
author: "Abhisek Gautam"
date: "30/08/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Introduction
We have planned to determine the rainfall in the place of the accident by taking data from the closest weather station. In order to do that, we will need to cross join the weather station data and accident's data and then find the distance between these two. The cross join returns m*n number of results. Then we will take only those readings contain minimum value of distance calculated.

## Installation of packages

``` {r install_load_libraries, results='hide', message=FALSE, warning=FALSE}
install.packages("tidyverse",repos = "http://cran.us.r-project.org")
install.packages("geosphere",repos = "http://cran.us.r-project.org")

library(tidyverse)
library(geosphere)
```

##Loading data into variables
Creating a dummy weather data
``` {r create_weather_data, results='hide', message=FALSE, warning=FALSE}
weather <- data.frame(
			 station_number= c(1121),
			 rainfall = c(10),
	     station_longitude= c(145),
	     station_latitude = c(-37)
	)
```

Loading accident data (only 1000 are loaded for the sake of example)
``` {r load_crash_data, results='hide', message=FALSE, warning=FALSE}
crashes <- read.csv("Crashes_Last_Five_Years.csv",nrows=1000)
```

##Perform a cross join
So now we will perform a cross join of the crash data and weather data

``` {r cross_join_data, results='hide', message=FALSE, warning=FALSE}
weather_crashes <- merge(weather, crashes %>% select(ACCIDENT_NO, ACCIDENT_DATE, LONGITUDE, LATITUDE), all= TRUE)
```

##Calculate the distance
Finally, we can get the distance by using the crossed data table.

``` {r distance_calculation, results='hide', message=FALSE, warning=FALSE}
weather_crashes_dist <- 
	weather_crashes %>% mutate(dist_station_crash = distHaversine(cbind(station_longitude, station_latitude), cbind(LONGITUDE, LATITUDE)))
```

##Our final data
We will obtain:

``` {r display_calculation }
head(weather_crashes_dist, 10)
```
